Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-04-22 papers/B1555_EdgeOn/B1555_letter.tex
add opt procedure

As a first trail of modelling, we create a single SIE model to 
justify the perforamnce of a simple lensing potential. Like previous studies
\citep{Marlow, Xu14}, flux anomaly in B1555+375 cannot be predcited
with a single elliptical lensing potential. 
We then create two separate models of the lensing potential.  In the
first we treat the lens as a SIE bulge and an exponential edge-on disk
(SIE+expdisk).  In the second model the disk is represented as a very
elongated SIE component (2-SIE).  The lens system is red, with a
strong jump in flux between the F814W (roughly I) and F160W (roughly
H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
$z_\ell = 1.0$ and a source redshift of $z_s =1.5$.  The full best-fit parameters are shown in Table
2. Both of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux
ratios. The comparison of observation and our lens modelling is given
in Figure 3 and Tables 3 \& 4.
[WHY NO EXTERNAL SHEAR?---WE THINK WITH ONLY RADIO DATA ITS LACK OF CONSTRAINT]

>>>>

As a first trail of modelling, we create a single SIE model to 
justify the perforamnce of a simple lensing potential. Consistent with previous studies
\citep{Marlow, Xu14}, our single elliptical potential model cannot predict flux anomaly in B1555+375. 
We then create two separate models of the lensing potential.  In the
first we treat the lens as a SIE bulge and an exponential edge-on disk
(SIE+expdisk).  In the second model the disk is represented as a very
elongated SIE component (2-SIE).  The lens system is red, with a
strong jump in flux between the F814W (roughly I) and F160W (roughly
H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
$z_\ell = 1.0$ and a source redshift of $z_s =1.5$. Our steps to explore the parameter space are: 1) Apply strong priors from SHARP AO image to the edge-on disk position angle and ellipticity, and use the best-fit model of \citet{marlow} as the start point of the bulge component and the source position. 2) Let all parameters without priors vary to reach a temporary best-fit. 3) Start with the best-fit in step 2 and let all parameters with priors vary to reach another best-fit (also ensure this best-fit is not far from the priors). 4) Let all parameters vary to reach the final optimal model. 
The full best-fit parameters are shown in Table
2. Both of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux
ratios. The comparison of observation and our lens modelling is given
in Figure 3 and Tables 3 \& 4.
[WHY NO EXTERNAL SHEAR?---WE THINK WITH ONLY RADIO DATA ITS LACK OF CONSTRAINT]
